Unsupervised Acquisition of Comprehensive Multiword Lexicons \\ using Competition in an $n$-gram Lattice

### 2017-05-29 reviewer_response.txt

We would like to thank all of our reviewers for their detailed comments. We have tried to address the important points as best we can, but we were limited to provided with 3 extra pages (beyond the 10 pages of the original submission), and because all the reviews had numerous suggestions for improvement with only one obvious overlap, we have had to pick and choose what we could add. In cases where we did not change the paper, threre is a justification below.

@@

>In terms of the methodology, a discussion is needed about the motivation for
adopting Brooke et al.'s lexical predictability ratio (LPR), and for the
modifications proposed, such as the use of minLPR instead of the product of
the LPRs and why the focus is on the weakest link (was there any comparison
between the use of minLPR and the product of LPRs, is it done for efficiency
reasons, etc).  Moreover, the construction of the lattice needs to be
explained, including how the nodes relate to one another. For instance, in
figure 2, the solid lines indicate subsumption, but "keep everything under
wraps" is linked with "be keep * under" via a subsumption relation, even
though the latter contains elements that are not in the former (shouldn't it
be an overlap link?).

We have added a bit more to the discussions of LPR, to be more explicit why LPR is a good metric for our lattice. We've also fixed the incorrect relations you mention, which should hopefully resolve the confusion.

>In terms of the evaluation, the distinction between contiguous and gapped
test sets, which are later merged into a single test set per language when
presenting the results, is not helpful. Instead, maintaining the distinction
would help clarify the advantages of the proposed approach in each language,
particularly in relation to the error analysis.

As we note in the paper, adding the distinction between continguous and gapped simply isn't defensible given the lack of positive gapped examples across some of the datasets (since both precision and recall rely on primarily on true positives). We would very much like to present this distinction, but the scores depend primarily on a handful of examples for some of datasets and the results are erratic, they would confuse rather than elucidate.

@@

Note that we are not ourselves proposing FS, we are borrowing the theory behind FS from the work of Wray (2002;2008), who includes an extremely thorough discussion of its relationship to other linguistic theories (Chapter 7 of the 2008
book in particular), including Construction Grammar. We have added a bit more detail to our introduction of FS to make it clear that, yes, most "constructions" are FS, and we have added constructions to Figure 1. However, ultimately
this is a technical paper, and we are limited in the space we can dedicate to theoretical concerns.

> The case of morphology is far less clear, however it is equally important,
and it has to do with the basic question of what is the unit that constructs
the FS (or the lattices themselves in empirical terms). Are these words?
morphemes? lemmas? POS? inflections? In the case  of words, what is the
relation of inflected sequences forms / inflected idioms (kicked his bucket
vs kicked her bucket, for instance) -- are they the same? related?
overalapping? subsumed?. As it stands, the discussion of morphology comes
out only later as an afterthought -- where the construction of the lattice
in Japanese (in the evaluation section) involves some morphological
segmentation whereas the lattice construction for the other languages
doesn't. It is thus unclear if the algorithm finds sequences that are of the
same type, or are comparable for that matter, across those languages. The
selected FS may be incomparable in terms of effective length (morpheme
sequences tend to be longer), the status of function words vs. inflection in
FS, and so on. The authors should put forth clearly what is the status of
morphology inside their general theory (and in terms of their regular
expressions), and then later revisit the empirical ramifications of their
decision -- for instance what happens when moving between typologically
different languages.

We have added a bit more to both the introduction of FS as well as a paragraph in the discussion that addresses this point. Ultimately, in all three languages we are tokenizing and lemmatizing using standards for each language, and building our FS from the result. However, this is not a theoretical choice, but a practical one; it is undeniable that FSes often involve morphological components that we are overlooking.  With Japanese, due to the lack of word boundaries, morphological segmentation is a more standard form of tokenization, and so we have taken advantage of this to bring Japanese somewhat closer to our theoretical ideal. Given that many of the case markers of Japanese correspond to prepositions in European languages (or the possesive marker in English), the actual difference in generated FS is fairly minor, except for the extra overhead of word segmentation in Japanese that is provided by word boundaries in English (in Wray's theory, most words would be FS by default).

@@

In the discussion, we have added a thorough analysis of specific examples and some statistics, including most of the information you ask for (implicitly if not explicitly).

> - Related to the previous point: While noting the distinction between FS and
MWEs, is it perhaps worth measuring recall against MWE datasets? Most MWEs
apart from proper names should count as FS, right?

Do you mean as a way of evaluating different systems built on the same corpus, or just to get a sense of coverage more generally? One central problem with using recall for evaluation is that in order to make it fair, there must be some control of the size of the lexicon. Neither our system nor our best performing competitors are ranking models, none of them offer an easy or fair way to simply take the best N words and look at recall. And even if they did, there's other kinds of biases that would come into play: for instance, PMI and similar metrics do well with rare terms that correspond well to the MWE lexicon of WordNet, for instance, which (at the type level) is dominated by certain kinds of terminology (biomedical terms, particularly) which are not really used outside a very specific community. This relates to a more fundamental problem with the idea of using recall in external lexicons as any kind of useful measure: we could not expect any particular corpus (even a very large one) to do justice to the full range of FS/MWE for a language, since most of which appear regularly only within specific genres. For example, we could not expect to build a good lexicon of English verb-particle constructions from a biomedical corpus, because many are too informal to be appropriate for that genre (e.g. "mess up"). With the qualitative analysis we have added, the genre-specificity of the FS we extra is hopefully more clear.

Though it perhaps does not directly address your comment (since it doesn't involve an external MWE lexicon), we were nonetheless inspired by your comments to include an analysis of the recall of MWE vs. non-MWE FS in the context of our existing ICWSM test set, and a small investigation of the recall (also in the ICWSM) of extremely common MWE from another MWE-annotated social media corpus.
